### 2015-05-06 latex/phd_thesis.tex
Remove proofreaders test

I owe an enormous debt of gratitude to my thesis writing buddies, Hannah Vanyai and Darcy Moore, who kept me going during tough times and to my thesis proof readers, Belinda Phipson, Saskia Freytag, Goknur Giner, and Dineika Chandrananda who have greatly improved this thesis.

>>>>

I owe an enormous debt of gratitude to my thesis writing buddies, Hannah Vanyai and Darcy Moore, who kept me going during tough times and to my thesis proofreaders, Belinda Phipson, Saskia Freytag, Goknur Giner, and Dineika Chandrananda who have greatly improved this thesis.
